The transition redshift as a probe of reionization

### 2019-08-12 paper/ms.tex
Add bit about generating the halo field

\subsection{[\OIII] intensity mapping} \label{ssec:oiii_int_map}
In order to model the relation between [\OIII] luminosity ($L_{\OIII}$) and
halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that
the mean luminosity of a halo of mass $M$ is,
\beq \label{eq:lum_mass_relation}
\avg{L}(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha}\text{,}
\eeq
where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
[\OIII] at that redshift and $\alpha$ is the power-law index. We then draw the
luminosity of each halo from a lognormal distribution of mean $\avg{L}(M)$ and
scatter $\sigma$. Once the average intensity is fixed (which we assume so),
this is a two-parameter model ($\alpha$ and $\sigma$) of the [\OIII]
luminosity-mass relation. In practice, the average intensity of the field only
enters in the detectability calculation, so we instead work in the convenient
units where $L_0=1$ and $M_0=10^{10}\,\Msun$.

>>>>

We generate the halo field using the included halo finder in \tfast{}. This
halo finder is a remnant of an earlier version of the code
\citep{2007ApJ...669..663M} and is typically unused in standard
configurations. It is based upon the ``peak-patch'' algorithm for halo finding
introduced by \citet{1996ApJS..103....1B}.

\subsection{Intensity mapping} \label{ssec:oiii_int_map}
In order to model the relation between luminosity ($L$) and
halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that
the mean luminosity of a halo of mass $M$ is,
\beq \label{eq:lum_mass_relation}
\avg{L}(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha}\text{,}
\eeq
where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
[\OIII] at that redshift and $\alpha$ is the power-law index. We then draw the
luminosity of each halo from a lognormal distribution of mean $\avg{L}(M)$ and
scatter $\sigma$. Once the average intensity is fixed (which we assume so),
this is a two-parameter model ($\alpha$ and $\sigma$) of the [\OIII]
luminosity-mass relation. In practice, the average intensity of the field only
enters in the detectability calculation, so we instead work in the convenient
units where $L_0=1$ and $M_0=10^{10}\,\Msun$.
